### 2011-01-28 docs/architecture/architecture.tex
add some notes on ghostcells

>>>>

Ghostcells are filled through a variety of different routines, depending
on the objective.

\item {\tt multifab\_fill\_boundary} fills ghost cells for two
  adjacent grids at the same level, which als includes periodic domain
  boundary ghost cells.

\item {\tt multifab\_physbc} fills ghostcells at the physical boundaries.

\item {\tt multifab\_fill\_ghost\_cells} is used for multilevel
  problems, and fills ghostcells in the finer grid (level {\tt n}) by
  interpolating from data in the coarser grid (level {\tt n-1}).

  This call is usually preceded by a call to {\tt
    ml\_cc\_restriction\_c} which sets the level {\tt n-1} data to be
  the average of the level {\tt n} data covering it.
